### 2024-05-16 getting-started.qmd
20240514 - cleanup
20240515 - callout
20240516 - section headings for cross-reference

# Getting Started with R for Data Analysis

@@

If you are in Dr. Petersen's class, also perform the following steps:

1. Set up a free account on [GitHub.com](https://github.com).
1. Download GitHub Desktop: <https://desktop.github.com/>

>>>>

# Getting Started with R for Data Analysis {#sec-gettingStarted}

@@

::: {#nte-gettingStarted .callout-note title="If you are in Dr. Petersen's class"}
If you are in Dr. Petersen's class, also perform the following steps:

1. Set up a free account on [GitHub.com](https://github.com).
1. Download GitHub Desktop: <https://desktop.github.com>
:::

### 2024-05-16 intro.qmd
20240514 - update
20240514 - todo
20240514 - cleanup
20240514 - embed video
20240516 - section headings for cross-reference

# Introduction

@@

## What is Fantasy Football? (#sec-whatIsFantasyFootball)

Fantasy football is an online game where participants assemble (i.e., “draft”) imaginary teams composed of real-life National Football League (NFL) players.
In this game, participants compete against their opponents (friends/coworkers/classmates), accumulating points based on players' actual statistical performances in games.
The goal is to outscore one’s opponent each week to win matches and ultimately claim victory in the league.

@@

Of course, this is not a traditional psychology textbook.
However, the class incorporates important psychological concepts, such as cognitive biases in judgment and prediction, etc.
In the modern world of big data, research and society need people who know how to make sense of the information around us.
Psychology is in a prime position to teach applied statistics to a wide variety of students, most of whom will not have careers as psychologists.
Psychology can teach the importance of statistics given humans’ cognitive biases.
It can also teach about how these biases can influence how people interpret statistics.
This course will teach readers the applications of statistics (prediction) and research methods (empiricism) to answer questions they find interesting, while applying scientific and psychological rigor.

@@

>>>>

# Introduction {#sec-intro}

@@

## What is Fantasy Football? {#sec-whatIsFantasyFootball}

Fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.
In this game, participants compete against their opponents (e.g., friends/coworkers/classmates), accumulating points based on players' actual statistical performances in games.
The goal is to outscore one's opponent each week to win matches and ultimately claim victory in the league.

@@

Of course, this is not a traditional psychology textbook.
However, the class incorporates important psychological concepts, such as cognitive biases in judgment and prediction, etc.
In the modern world of big data, research and society need people who know how to make sense of the information around us.
Psychology is in a prime position to teach applied statistics to a wide variety of students, most of whom will not have careers as psychologists.
Psychology can teach the importance of statistics given humans' cognitive biases.
It can also teach about how these biases can influence how people interpret statistics.
This course will teach readers the applications of statistics (prediction) and research methods (empiricism) to answer questions they find interesting, while applying scientific and psychological rigor.

@@

::: {.content-visible when-format="html"}

![Benjamin Motz on statistics and fantasy football course](images/motzVideo.mp4){width=100%}

:::
